---
title: "coverage_summary"
output: html_document
date: "2023-03-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Calculate coverage statistics

```{r}
library(dplyr, warn.conflicts = FALSE)
library(tilt.company.match)

# TODO: Replace with the path/to/your/real/to_edit.csv
to_edit <- read.csv("to_edit.csv")
to_edit

suggested <- to_edit %>%
  filter(suggest_match)

# Number of matched companies based on suggested matches
matched_rows <- suggested %>% nrow()
matched_rows

# Share of matched companies from total loanbook companies
total_rows <- loanbook %>%
  distinct(company_name) %>%
  nrow()
matched_share <- matched_rows / total_rows
matched_share
```

## Number and share of matched companies classified by misc_info from total loanbook companies

misc_info should be replaced with variables like sectors, headcount etc.

```{r}
x <- loanbook %>% count(misc_info)
y <- suggested %>% count(misc_info)
misc_share <-
  left_join(x, y, by = c("misc_info"), suffix = c("_loanbook", "_merged")) %>%
  mutate(n_share = n_merged / n_loanbook)
```

## Calculate loan exposure categorised based on misc_info 

id_tilt column is used as the substitute due to unavailability of loan amount
column in sample data. Please replace id_tilt column with the loan amount
column.

```{r}
# Calculate number of loans and their share from total after grouping by
# misc_info
exposure_count <- suggested %>%
  count(misc_info) %>%
  mutate(count_share = n / sum(n))

# Calculate sum of loan values and their share from total value after grouping
# by misc_info
exposure_sum <- suggested %>%
  group_by(misc_info) %>%
  summarise(sum_expo = sum(id_tilt)) %>%
  mutate(sum_share = sum_expo / sum(sum_expo))
```
